---
title: "HLM models for conjoint analysis"
output: html_notebook
---
The code from Chapter 9 of Chapman and Feit are reproduced here... The goal is to learn the output of HLM models

```{r,message=F}
library(dplyr)
library(magrittr)
conjoint.df <- read.csv("http://goo.gl/G8knGV")
# inspect the data frame
skimr::skim(conjoint.df)

```

Rating is continuous variable the rest of the integer type variables are categorical (Ignoring resp.id).

```{r}
conjoint.df %<>% 
  mutate(height = as.factor(height),
         speed = as.factor(speed)) %>% 
  as_tibble(.)

# number of respondents
conjoint.df %>% distinct(resp.id) %>% summarise(N = n()) -> N
```

There are `r N` respondents in this study

```{r}
lattice::histogram(~rating|height,data = conjoint.df)
```

# Linear model

```{r}
ride.lm <- lm(rating ~ . - resp.id, data = conjoint.df)
summary(ride.lm)
plot(ride.lm)
```

The most desired coaster based on the coefficients is Speed of 70, height 300, const of steel and Dragon themed
The sum of the coefficents 3.07307 + 4.48697 +  2.94551 exceed the max rating of 10. 

Interpretting the model based on the averages that include the desireable and undesirable effects may be misleading at the extremes. So, what do we do?
