---
title: "Choice Modeling - Solo2"
author: "Sri Seshadri"
date: "11/2/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(dplyr)
```

# Data Set up

```{r}
load("stc-cbc-respondents-v3(1).RData")
library(dummies)
load("efCode.RData") 
taskV3 <- read.csv("stc-dc-task-cbc -v3(1).csv", sep="\t")

task.mat <- as.matrix(taskV3[, c("screen", "RAM", "processor", "price", "brand")])
task.mat <- cbind(task.mat,rep(1:36,each = 3))
task.mat <- cbind(task.mat, rep(1:3,times = 36))
colnames(task.mat)[6] <- "choiceset"
colnames(task.mat)[7] <- "option"
X.mat=efcode.attmat.f(task.mat) #  I hate this, let make it better 

designset <- matrix( rep( t( task.mat ) , 424 ) , ncol =  ncol(task.mat) , byrow = TRUE )
colnames(designset) <- c(colnames(task.mat))
expandresp <- function(choice){
  switch (choice,
    "1" = return(c(1,0,0)),
    "2" = return(c(0,1,0)),
    "3" = return(c(0,0,1))
  )
}

stackresp <- function(rowid){
  unlist(purrr::map(resp.data.v3[rowid,4:39],expandresp))
}

designset <- cbind(designset,unlist(purrr::map(1:424,stackresp)))
colnames(designset)[8] <- 'choice'

designset <- cbind(designset,rep(resp.data.v3$record,each = 108))
colnames(designset)[9] <- 'Respondent'

designset <- as_tibble(designset)
  
```

# EDA

```{r}
skimr::skim(designset)
```

```{r}
SummaryData <- designset %>% 
  group_by(choiceset,option) %>% 
  summarise(Counts = sum(choice)) %>% 
  ungroup() %>% 
  mutate(choiceset = as.factor(choiceset),
         PrefPercent = round(Counts/424,2),
         interested = ifelse(PrefPercent >=0.70,2,ifelse(PrefPercent <= 0.12,0,1)))

lattice::barchart(option ~ Counts | choiceset , data = SummaryData)
```

## What are people liking

```{r}
taskV3$choice.set <- as.factor(taskV3$choice.set)
SummaryData %>% 
  filter(interested == 2) %>% 
  arrange(desc(PrefPercent)) %>% 
  distinct(choiceset,option) %>% 
  dplyr::left_join(.,taskV3,by = c("choiceset" = "choice.set",
                                   "option"= "choice.ID")) %>% 
  mutate(LevelsTech = paste0(as.character(screen),as.character(RAM), as.character(processor)),
         LevelsTechPrice = paste0(LevelsTech,as.character(price)),
         LevelsTechbrand = paste0(LevelsTech,as.character(brand)))
```

Observations are:

1. 16GB RAM is very popular
2. 2.5 and 2 GHz Processor is preferred
3. Price of $199 
4. Higher price is paid ($299) for larger screen( upgrade from 7" to 10"; RAM being 16GB and Processor being 2 GHz)
5. STC brand appreared in 4 of the 9 popular comninations, followed by pear (3/9)

# What are people not liking

```{r}
SummaryData %>% 
  filter(interested == 0) %>% 
  arrange(PrefPercent) %>% 
  distinct(choiceset,option) %>% 
  dplyr::left_join(.,taskV3,by = c("choiceset" = "choice.set",
                                   "option"= "choice.ID")) %>% 
  mutate(LevelsTech = paste0(as.character(screen),as.character(RAM), as.character(processor)),
         LevelsTechPrice = paste0(LevelsTech,as.character(price)),
         LevelsTechbrand = paste0(LevelsTech,as.character(brand))) -> Lows

 ggplot(Lows,mapping = aes(x = as.factor(processor))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(brand))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(price))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(RAM))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(LevelsTech))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(LevelsTechPrice))) + geom_bar()
 ggplot(Lows,mapping = aes(x = as.factor(LevelsTechbrand))) + geom_bar()
```

Observations are:

1. 1.5 GHz is amongst the least popular
2. STC is NOT UNPOPULAR (wow!)
3. 

# Main effects?

```{r}
SummaryData %>% 
  #filter(interested == 2) %>% 
  #arrange(desc(PrefPercent)) %>% 
  #distinct(choiceset,option) %>% 
  dplyr::left_join(.,taskV3,by = c("choiceset" = "choice.set",
                                   "option"= "choice.ID")) %>% 
  mutate(LevelsTech = paste0(as.character(screen),as.character(RAM), as.character(processor)),
         LevelsTechPrice = paste0(LevelsTech,as.character(price)),
         LevelsTechbrand = paste0(LevelsTech,as.character(brand))) -> DOE

 DOE %>% 
  ggplot(mapping = aes(x = as.factor(screen), y = PrefPercent)) + geom_violin()
 
DOE %>% 
  ggplot(mapping = aes(x = as.factor(price), y = PrefPercent)) + geom_violin()
DOE %>% 
  ggplot(mapping = aes(x = as.factor(brand), y = PrefPercent)) + geom_violin()
DOE %>% 
  ggplot(mapping = aes(x = as.factor(RAM), y = PrefPercent)) + geom_violin()
DOE %>% 
  ggplot(mapping = aes(x = as.factor(processor), y = PrefPercent)) + geom_violin()
DOE %>% 
  ggplot(mapping = aes(x = as.factor(price*brand), y = PrefPercent)) + geom_violin()
DOE %>% 
  ggplot(mapping = aes(x = as.factor(paste0(as.character(price),".",as.character(brand))), y = PrefPercent)) + geom_violin()
```
# MCMC modeling

```{r}
# making the design parameters as factor variables
designset %<>%
 mutate_if(is.numeric,as.factor) 

# using library(mlogit)
library(mlogit)

cbc.mlogit <- mlogit.data(data = designset, 
                          choice = "choice",
                          shape = "long",
                          varying = 1:5,
                          alt.levels = 1:3,
                          id.var = "Respondent")

m1 <- mlogit(choice ~ screen + RAM + processor + price + brand , data = cbc.mlogit)
summary(m1)
```

